---
title: "Unit1_Rprogramming_Assignment"
---

1. Calculate the following 
  a.Σ a <- 5:100 (a^4 + 5*a^3) with and without loop 
    WITH LOOP 
```{r}
sum <- 0
for (a in 5:100) {
  sum <- sum + (a^4 + 5*a^3)
}
sum
```
   WITHOUT LOOP 
```{r}
b <- 5:100 
sum(b^4 + 5*b^3)

```

  b. Calculate U40 which Un = Un-1 + Un-2 with U(1)=1 and U(2)=2
```{r}
fibonacci <- numeric(40)
fibonacci[1] <- 1
fibonacci[2] <- 2
for (n in 3:40) {
  fibonacci[n] <- fibonacci[n-1] + fibonacci[n-2]
}
fibonacci
```

  c. Write a program to calculate cos x, sin x(Taylor series) , Get the input(x) from the user and n=45.
```{r}
x <- as.numeric(readline(prompt="Enter value of x: "))
n <- 45
cosn <- 0
sinn <- 0
cosx <- 0
sinx <- 0
for (i in 0:n) {
  cosn <- (-1^n) * (x^(2*n))/ factorial(2*n)
  cosx <- cosx +  cosn
  sinn <- -1^(n) * x^(2*n + 1)/ factorial(2 * n + 1)
  sinx <- sinx +sinn
}
cosx
sinx
```
  d. Create a vector of the values of e cos(x) at x = 3, 3.1, 3.2, . . . , 6.
```{r}
x = seq(3,6 , by=0.1)
ecos <- c(exp(x) * cos(x))
ecos
```
  
  e. x <- 1:300. How many numbers in x are divisible by 2
```{r}
count <- 0
for (x in 1:300) {
  if(x %% 2 == 0){
    count <- count + 1
  }
}
count
```

2. Solve the following system of linear equations using Gaussian elimination (Ax=y)
  x + 2y + 3x = 9
  2x - y + 2z = −3
  3x + 3y + z = 5
```{r}
A <- matrix(c(1, 2, 3,
              2, -1, 2,
              3,  3, 1), 3, 3, byrow=TRUE)
B <- c(9, -3, 5)
solution <- gaussianElimination(A, B)
solution
```

3. Use outer function to create matrix
```{r}
x <- 0:4
y <- 0:4
mat <- outer(x,y, function(x,y) x+1*y)
mat
```

4. Get the COVID-19 Dataset from the data sources. Number of observations should be more than 100.Then, report the following informations

  a. Data source detail 
  Title: COVID19 Daily Updates
  Link: https://www.kaggle.com/gpreda/coronavirus-2019ncov
```{r}
c19_dataset <- read.csv("D:\\study\\Fourth year\\Data sciense\\Dataset\\archive\\covid-19-all.csv")
c_dataset <- c19_dataset
c_dataset
```
  
  
  b. Explain the unit & necessity of each veriable
  _ Country/Region: Country or Region; ex: Mainland China, Romania, Italy
  _ Province/State: Province or State; ex: Hubei
  _ Latitude: Latitude of the Country
  _ Longitude: Longitude of the Country
  _ Comfirmed: Confirmed number of cases
  _ Recovered: Number of recovered patients
  _ Deaths: Number of deaths
  _ Date: Date of the report
```{r}
colnames(c_dataset)
```
 
  c. Find the missing values(rows & columns) and replace them with mean(Tidy Dataset)
```{r}
# find the missing value
is.na(c_dataset) 
# the dataset have empty value but don't have missing value

#replace the missing value 

x <- c_dataset$Deaths
x[which(is.na(x))] <- mean(x, na.rm = TRUE)
c_dataset

c_dataset[] <- lapply(c_dataset, function(x) { 
  x[is.na(x)] <- mean(x, na.rm = TRUE)
  x
})
c_dataset 
# there is nothing to replace since the dataset don't have missing value
```
 
  
  d. Generate the two new variables(Var1:Mean, Var2: Median from available variable)
```{r}
c_dataset %>% mutate(Mean=mean(Latitude),Median=median(Latitude))
c_dataset
```

  
  e. Rename the two existing variables 
```{r}

c_dataset %>% rename("Country/Region"=Country.Region, "Province/State"=Province.State,)
```
  
  f. Create a plot using following instructions (using 7 layers of Grammar of Graphics)
    i. Choose x and y axis(aes)
```{r}
# Choose Date as X and Confirmed_cases Y
confirmed_cases <- c_dataset %>% group_by(Date) %>% count(Date, wt = Confirmed)
Date <- confirmed_cases[['Date']]
Confirmed <- confirmed_cases[['n']]
confirmed_cases
```
  
    ii. geom_point() - specify the parameters, size : 5, color: red, alpha: ⅕ 
  
```{r}
gp = geom_point(alpha=1/5, color="red", size=5)
gp
plot <- ggplot(x = confirmed_cases, mapping = aes(x = Date, y = Confirmed)) + gp
plot
```

    iii. Use Facet grid, cartesian coordinates & geom_smooth()
```{r}
# facet grid
plot + facet_grid(Confirmed)
```

```{r}
# coord_cartesian
plot + coord_cartesian(expand = FALSE)
```

```{r}
# geom_smooth
plot + geom_smooth()
```

    iv. Assign the title to x, y and graph 

```{r}
plot <- plot + ggtitle("The number of confirmed cases") + xlab("Date") + ylab("Confirmed cases")
plot
```

    v. Export the graph to your working directory with the title called “covid_19_ dataset.png”

```{r}
ggsave(filename = "D:\\study\\Fourth year\\Data sciense\\Dataset\\archive\\covid_19_positive_cases_dataset.png", units = "cm", width = 40, height = 25)
```

