---
title: "Data science midterm exam"

---

1.Write a R code to Generate 6X6 matrix (A) using the random numbers between 1 to 100 & generate another 6x6 matrix (B) using random numbers between 500 to 600.
```{r}
x <- sample(1:100)
y <- sample(500:600)
A <- matrix(x, 6, 6)
B <- matrix(y, 6, 6)

A
B

```

a.	Find the range of matrices A and B.
```{r}
range(A)
range(B)
```

b.	Find the max value from each row of the matrices A and B.(using the apply function. syntax: apply(Matrix_name,margin,method). margin 1 = row, margin 2 = column)
```{r}
apply(A,1,max)
apply(B,1,max)
```

c.	Find the diagonal values of matrices A&B. (find the diagonal using diag() function)
```{r}
diag(A)
diag(B)
```

d.	Multiply matrices A and B
```{r}
A%*%B
```

e.	Replace the 4th row of Matrix A with diagonal values of matrix B
```{r}
A[4, ] <- diag(B)
A
```

f.	Multiply matrices A & B and store the values on X.
```{r}
X <- A %*% B
X
```

g.	Divide the matrix A with matrix B.
```{r}
A %*% solve(B)
```

2. Create a table using dataframe/tibble with the following categories(a to f) And input at least 10 samples(observation)

a.	First name, 
```{r}
a <- c('Hewson', 'Hornby','Sarkisian','Melville','Hudson','Sumner','Rihanna','Lanzoni', 'Nelson','Arantes')
```

b.	Second Name, 
```{r}
b <- c('David','Lesley','Cherilyn','Richard','Saul','Gordon','Robyn','Fabio','Rogers','Edison')
```

c.	Age,
```{r}
c <- c(11,12,13,26,56,67,78,23, 45,34)
```

d.	Occupation, 
```{r}
d <- c('student','office','freelancer','designer','baker','engineer','farmer','student','seller','seller')
```

e.	Place,
```{r}
e <- c('PP','KPC','SR','BKK','TK','TTB','PS','PP','KP','TTY')
```

f.	Random numbers( between 1 to 10)
```{r}
f <-sample(1:10)
table <- data.frame(First_name = a, Second_name = b, Age = c, Occupation = d, Place = e, Random_number = f)
table
```

g.	Extract the last column (f)
```{r}
last_col <- table$Random_number
last_col
```

h.	Find the sum, mean and length of the extracted column
```{r}
sum(last_col)
mean(last_col)
length(last_col)
```
3. Create a .txt file (Minimum : 150 words) with the latest news (In English) in cambodia from the official news agency’s website(Note: Include the reference link) and do the following

a.	Read the .txt file
```{r}
library(tokenizers)
newsFile <- read.delim("D:\\study\\Fourth year\\Data sciense\\News.txt")
newsFile 
```

b.	Perform the Tokenization & count the words
```{r}
data <- paste0(newsFile)

tokenization <- tokenize_words(data)
tokenization

count <- count_words(data)
count
```

c.	Identify the most repeated word and replace that word with “KIT”
```{r}
repeated_words <- names(table(tokenization))[as.vector(table(tokenization))==max(table(tokenization))]
repeated_words
repeated_words_count <- max(table(tokenization))
repeated_words_count

replace <- gsub(repeated_words, "KIT", data)
replace
```

d.	Perform the Sentiment analysis
```{r}
library(sentimentr)
library(qdap)
library(dplyr)
library(tidytext)
#To know number of sentences and words
step_1 <- sentiment(replace)
step_1

#Total number of words
step_2 <- sentiment_by(replace)
step_2

#To display the sentences
step_3 <- get_sentences(replace)
step_3

#find emotion at the sentence level
step_4 <- emotion(replace)
step_4

#Aggregated emotion by group
step_5 <- emotion_by(replace)
step_5

#Find profanity at the sentence level
step_6 <- profanity(replace)
step_6

#Aggregated profanity by group
step_7 <- profanity_by(replace)
step_7
```

e.	Plot the graph between “words count” and “words” using geom_col()
e.1. X-axis title =“Number of words”, Size=10, Bold, Text in Blue color, Center, space between graph and title = 20.
e.2. Y-axis title =“List of words”, Size=10, Bold, Text in Red color, Center, space between graph and title = 20.
e.3. Graph title =”Text Mining using R”,Size = 25, Bold, Center, Text in Yellow color, space between graph and title = 25.

```{r}
#table setup 
text_df <- data.frame(text = data)
text_df

library(magrittr)
text_words <- text_df %>% unnest_tokens(output = word, input = text) 
text_words

#word count
text_wordcounts <- text_words  %>% count(word, sort = TRUE)
text_wordcounts

#plot the data 
library(ggplot2)
graph <- ggplot(data = text_wordcounts, aes(word, n)) + geom_col()
graph

#e.1. X-axis title =“Number of words”, Size=10, Bold, Text in Blue color, Center, space between graph and title = 20.
graph <- graph + xlab('Number of word') + theme(axis.title.x=element_text(size=10,color='blue', face='bold', hjust=0.5, margin=margin(r=20)))
graph

#e.2. Y-axis title =“List of words”, Size=10, Bold, Text in Red color, Center, space between graph and title = 20.
graph <- graph + ylab('List of words')+ theme(axis.title.y=element_text(size=10,color='red', face='bold', hjust=0.5, margin=margin(r=20)))
graph

#e.3. Graph title =”Text Mining using R”,Size = 25, Bold, Center, Text in Yellow color, space between graph and title = 25.
graph <- graph + ggtitle('Text Mining using R')+ theme(plot.title=element_text(size=25, color='yellow', face='bold', hjust=0.5, margin=margin(r=25)))
graph
```

4. Find the assigned Dataset from the list below and perform the following
link: Bad Drivers https://github.com/fivethirtyeight/data/blob/master/bad-drivers/bad-drivers.csv
```{r}
#a.	Import and Clean the dataset.
library(tidyverse)
# import the data from github by using the link after click the raw button
dataset <- read_csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/bad-drivers/bad-drivers.csv")
dataset
names(dataset)
#clean the dataset 
#check if the data contain any NA value
check <- is.na(dataset)
check #the dataset don't have any NA value (return false for all row)

#b.	Find the x and y variables(axis) from the assigned dataset and give the reason for selecting the x and y axis. 
# choose Percentage Of Drivers Involved In Fatal Collisions Who Were Speeding as x and Percentage Of Drivers Involved In Fatal Collisions Who Were Alcohol-Impaired as y because we want to compare and show the change between those two data column
plot <- ggplot(dataset, aes(x=`Percentage Of Drivers Involved In Fatal Collisions Who Were Speeding`, y=`Percentage Of Drivers Involved In Fatal Collisions Who Were Alcohol-Impaired`))
plot

#c.	Plot the graph using geom_col() and perform the linear model in statistics.
plot <- plot+ geom_col()+ geom_smooth(method = lm)
plot

#d.	Perform the facet with the available columns(Choose the any two variables from the columns)
plot <- plot+ facet_grid(`Percentage Of Drivers Involved In Fatal Collisions Who Were Not Distracted` ~ `Percentage Of Drivers Involved In Fatal Collisions Who Had Not Been Involved In Any Previous Accidents`)
plot

#e.	Use the theme layer to do the following (Note: Based on dataset, name the x and y axis & graph)
#e.1. x-axis title =“________”, Size=10, Bold, Text in Green color, Center, space between graph and title = 20.
plot <- plot + xlab('Who were speeding') + theme(axis.title.x=element_text(size=10,color='green', face='bold', hjust=0.5, margin=margin(r=20)))
plot

#e.2. y-axis title =“________”, Size=10, Bold, Text in Yellow color, Center, space between graph and title = 20.
plot <- plot + ylab('Who Were Alcohol-Impaired')+ theme(axis.title.y=element_text(size=10,color='yellow', face='bold', hjust=0.5, margin=margin(r=20)))
plot

#e.3. Graph title =”_________”,Size = 25, Bold, Center, Text in Blue color, space between graph and title = 25.
plot <- plot + ggtitle('Percentage Of Drivers Involved In Fatal Collisions')+ theme(plot.title=element_text(size=25, color='blue', face='bold', hjust=0.5, margin=margin(r=25)))
plot

#save file
ggsave(filename="Percentage Of Drivers Involved In Fatal Collisions.png", units="cm", width=25, height=25)
```

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
